Representation theory and combinatorics are two important areas of mathematics. 
Kostka numbers and Littlewood-Richardson coefficients appear in both \cite{narayanan2006complexity}. 
They have a close connection to symmetric functions and Schur functions. 

One such symmetric Schur function are Gelfand-Tsetlin patterns \cite{StanleyEC2}. 
These patterns form $\mathcal{H}$-polytopes, and a conjecture states that the Ehrhart polynomials of so called Gelfand-Tstelin polytopes have non-negative rational coefficients \cite{KingTolluToumazet2004}. 
As far as we are aware, this conjecture have neither been proven or disproven. 

In this thesis, we investigate the Ehrhart polynomials of Gelfand-Tsetlin polytopes. 
Using computational power, over 1800 Gelfand-Tsetlin patterns were generated, from which polytopes were created and their Ehrhart polynomials computed. 
A limitation of the computations is the CPU-time needed to get the $h^*$-polynomials needed to get the Ehrhart-polynomials. 
Only Ehrhart polynomials with positive coefficients was found. 

The strucutre of thesis is as follows: the first section, Section \ref{polytopes}, gives a background to polytopes and Ehrhart theory. 
Section \ref{symfuncs}, describes symmetric functions with regards to semistandard Young tableaux. Section \ref{gt}, describes the bijection between semistandard Young tableaux and Gelfand-Tstelin patters, as well as introduces Gelfand-Tstelin polytopes. 
In Section \ref{method}, the method used to generate the Gelfand-Tstelin patterns and the Ehrhart polynomials are described. In the last section, Section \ref{results}, the results are presented. 